---
title: "2018-11-27 Baltimore Bridges 2018-12-06"
author: "zpb"
date: "December 6, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#clean data & load up some packages
```{r}
set.seed(6942069)
library(tidyverse)
library(scales)
library(forcats)
library(splines)
library(broom)
theme_set(theme_light())

maryland_bridges <- read_csv("https://raw.githubusercontent.com/zpbillman/Tidy_Tuesday/master/2018-12-06%20Baltimore%20Bridges/baltimore_bridges%5B1%5D.csv") %>%
  select(-vehicles) %>%
  filter(yr_built >= 1900) %>%
  replace_na(list(responsibility = "Replaced by tidyr")) %>%
  mutate(
    county = replace(county, county == "Baltimore city", "Baltimore City"),
    inspection_yr = inspection_yr + 2000,
    decade = 10 * (yr_built %/% 10),
    responsibility = fct_lump(responsibility, 4)
    )
```

#histogram of bridges built after 1880
```{r}
maryland_bridges %>%
  count(semidecade = 5 * (yr_built %/% 5)) %>%
  ggplot(aes(x = semidecade, y = n)) +
  geom_histogram(stat = "identity") +
  expand_limits(y = 0) +
  labs(
    y = "Number of Bridges built in Maryland per 5 years",
    x = ""
    )
```

#count by decade
%/% is integer division which just divides by the number after the operator and leaves no remainder
e.g. 22 %/% 10 = 2 & 132 %/% 10 = 13
```{r}
maryland_bridges %>%
  count(decadeBuilt = 10 * (yr_built %/% 10))
```

#Age of bridge relationship with condition
```{r}
maryland_bridges %>%
  group_by(decade) %>%
  summarize(
    pct_good = mean(bridge_condition == "Good"),
    total = n()
    ) %>%
  ggplot(aes(x = decade, y = pct_good)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(labels = percent_format()) +
  expand_limits(y = 0) +
  labs(
    y = "Percent bridges in Maryland that are rated 'Good'",
    x = ""
    )
```

Most bridges built before 1970 aren't great. The vast majority of bridges after 2000 are Good. 

```{r}
maryland_bridges %>%
  group_by(decade) %>%
  summarize(
    pct_good = mean(bridge_condition == "Good"),
    total = n()
    ) %>%
  ggplot(aes(x = decade, y = pct_good)) +
  geom_line() +
  #geom_smooth(method = "lm") +
  scale_y_continuous(labels = percent_format()) +
  expand_limits(y = 0) +
  labs(
    y = "Percent bridges in Maryland that are rated 'Good'",
    x = ""
    )
```


#Responsibility of roads
Notice to change the NAs to something else we needed to do a list. I don't know why :|
```{r}
maryland_bridges %>%
  replace_na(list(responsibility = "Other")) %>%
  count(responsibility = fct_lump(responsibility, 4), sort = TRUE) %>%
  mutate(responsibility = reorder(responsibility, n)) %>%
  ggplot(aes(x = responsibility, y = n)) +
  geom_col() +
  coord_flip()
```

#Rating by responsibility
```{r}
maryland_bridges %>%
  replace_na(list(responsibility = "Other")) %>%
  group_by(
    responsibility = fct_lump(responsibility, 4),
    decade
    ) %>%
  summarize(
    pct_good = mean(bridge_condition == "Good"),
    total = n()
    ) %>%
  filter(responsibility != "Other") %>%
  ggplot(aes(x = decade, y = pct_good, color = responsibility)) +
  geom_line() + 
  scale_y_continuous(labels = percent_format()) +
  expand_limits(y = 0) +
  labs(
    y = "Precentage of bridges in Maryland rated 'Good' by responsibility",
    x = "")
```

#Traffic
To get a nice looking 10^.x scales there is a link in R>General>How to use exponents...
```{r}
maryland_bridges %>%
  ggplot(aes(avg_daily_traffic)) +
  geom_histogram() +
  scale_x_log10(labels = comma)
```

#Summary of quintiles
quintiles determined by quantile(avg_daily_traffic, c(0, .2, .4, .6, .8, 1))
```{r}
maryland_bridges %>%
  filter(yr_built >= 1990) %>%
  group_by(traffic_category = cut(avg_daily_traffic, c(0, 1400, 6821, 16752, 42559, Inf))) %>%
  summarize(
    pct_good = mean(bridge_condition == "Good"),
    total = n()
    )
```

#How does traffic affect how well maintained a brdige is?
using ntile(value, n) breaks a set of data into its n tiles. Here I use 5 for quintiles
Required to set quintile as a character to get ggplot to read them as descrete
```{r}
maryland_bridges %>%
  mutate(traffic_quintile = as.character(ntile(avg_daily_traffic, 5))) %>%
  group_by(
    traffic_quintile,
    decade
    ) %>%
  summarize(
    pct_good = mean(bridge_condition == "Good"),
    total = n()
    ) %>%
  ggplot(aes(x = decade, y = pct_good, color = traffic_quintile)) +
  geom_line()
```

#making a map for the first time ever!
The call to arrange() puts the high values later
```{r}
maryland_bridges %>%
  arrange(avg_daily_traffic) %>%
  ggplot(aes(x = long, y = lat, color = avg_daily_traffic)) +
  borders("state", regions = "Maryland") +
  geom_point() +
  scale_color_viridis_c(direction = -1,
                        labels = comma_format()) +
  coord_map() +
  theme_void()
```

#Practice with log10 transformation of gradient
```{r}
maryland_bridges %>%
  arrange(avg_daily_traffic) %>%
  ggplot(aes(x = long, y = lat, color = avg_daily_traffic)) +
  borders("state", regions = "Maryland") +
  geom_point() +
  scale_color_gradient2(low = "blue", 
                        high = "red",
                        midpoint = log10(median(maryland_bridges$avg_daily_traffic)),
                        trans = "log10",
                        labels = comma_format()) +
  coord_map() +
  theme_void()
```

#Bridges on map colored by county
```{r}
maryland_bridges %>%
  ggplot(aes(x = long, y = lat, color = county)) +
  borders("state", regions = "Maryland") +
  geom_point() +
  scale_color_brewer(palette = "Dark2") +
  coord_map() +
  theme_void()
```

#County responsibility on precentage of bridges rated 'Good' by year
```{r}
maryland_bridges %>%
  group_by(
    county,
    decade
    ) %>%
  summarize(
    pct_good = mean(bridge_condition == "Good"),
    total = n()
    ) %>%
  ggplot(aes(x = decade, y = pct_good, color = county)) +
  geom_line() + 
  scale_y_continuous(labels = percent_format()) +
  expand_limits(y = 0) +
  labs(
    y = "Precentage of bridges in Maryland rated 'Good' by county",
    x = "")
```


#Effect of county responsibilty and time on bridge condition
Need to put data = ., otherwise it would pipe this dataframe right into the start
```{r}
maryland_bridges %>%
  mutate(good = bridge_condition == "Good") %>%
  glm(good ~ yr_built, data = .) %>%
  summary()
```

#Now to model it
augment takes the original data and models it with a new column called fitted
A lot of the augment shit you need to tell it the type of prediction to make
augment accepts a model object and adds that information to the original dataset
```{r}
#fit a logistic model
simple_model <- maryland_bridges %>%
  mutate(good = bridge_condition == "Good") %>% #adds column that shows status of Good as True or False
  glm(good ~ yr_built, data = ., family = "binomial")

augment(simple_model, maryland_bridges, type.predict = "response") %>%
  ggplot(aes(yr_built, .fitted)) +
  geom_line() +
  expand_limits(y = 1)
```

Same type of model, but now with more degrees of freedom
Change the 2 to see different types of shapes and better understand DOF
```{r}
dof_model <- maryland_bridges %>%
  mutate(good = bridge_condition == "Good") %>% #adds column that shows status of Good as True or False
  glm(good ~ ns(yr_built, 4), data = ., family = "binomial")

augment(dof_model, maryland_bridges, type.predict = "response") %>%
  ggplot(aes(yr_built, .fitted)) +
  geom_line() +
  expand_limits(y = 1)
```

consider a spline fit for this same regression
ns(yr_built, 4) gives 4 degrees of freedom
+ responsibility allows responsibility to linearly affect it
You can then use the color to pull them apart and see how that variable affects the model
Year and responsibilty are not allowed to interact with each other in this model
Goodness vs year, goodness vs responsibility, goodness vs county all put together
```{r}
respYRcnty_model <- maryland_bridges %>%
  mutate(good = bridge_condition == "Good") %>%
  glm(good ~ ns(yr_built, 4) + responsibility + county, data = ., family = "binomial")

augment(respYRcnty_model, maryland_bridges, type.predict = "response") %>%
  ggplot(aes(yr_built, .fitted, color = responsibility)) +
  geom_line() +
  facet_wrap(~ county) +
  scale_y_continuous(labels = percent_format()) +
  labs(y = "Predicted probability a bridge built in a given decade will be rated 'Good'")
```

There are not significant differences between shit though LOL

Removed influence of county from above plot
```{r}
respYR_model <- maryland_bridges %>%
  mutate(good = bridge_condition == "Good") %>%
  glm(good ~ ns(yr_built, 4) + responsibility, data = ., family = "binomial")

augment(respYR_model, maryland_bridges, type.predict = "response") %>%
  ggplot(aes(yr_built, .fitted, color = responsibility)) +
  geom_line() +
  scale_y_continuous(labels = percent_format()) +
  labs(y = "Predicted probability a bridge built in a given decade will be rated 'Good'")
```

Above plot but with predictive estimates
Notice mutate(reorder()) vs arrange(). Arrange controls dropping points on the paper, but not the order of factors
```{r}
respYRcnty_model %>%
  tidy(conf.int = TRUE) %>%
  filter(str_detect(term,"responsibility|county")) %>%
  mutate(term = reorder(term, estimate)) %>%
  ggplot(aes(y = term, x = estimate)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high))
```

In a given year, the odds of a bridge having a rating of good because of who is responsible
```{r}
respYR_model %>%
  tidy(conf.int = TRUE) %>%
  filter(str_detect(term,"responsibility")) %>%
  mutate(term = reorder(term, estimate)) %>%
  ggplot(aes(y = term, x = estimate)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high))
```

